Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-02-28 src-latex/parts/30-dataset.tex
WIP rebuttal
Ref to fig. 1 + mention to thumbnails

The directories are available from different libraries in Paris and have been digitised independently in various levels of quality. 
They cover a large period of time and originate from several publishers.
Therefore, their contents, indexes, layouts, methods of printing, etc. may vary a lot from one directory to another (see Figure \ref{fig:directories}).
We want our groundtruth dataset to be representative of the diversity of directories available in the period.

@@

%1. Entrée/Sortie de l'OCR
\textbf{OCR stage.} The first stage of the pipeline aims at extracting the raw text from the images. An OCR system runs
on the thumbnails of each segmented entry to extract its text. An entry might span over multiple text lines but is
always a single block. Thus, the most adapted mode is chosen when the OCR system allows for the detection mode (e.g. the
\emph{block} mode for \emph{Tesseract}). 
Some glyphs used in this dataset might be unknown to the OCR, and some like
\scalerel*{\includegraphics{./images/LH.png}}{H} do not even have a Unicode codepoint, and were annotated using Unicode Private User Area 1.
Furthermore, as some annotations guidelines where unclear to human annotators, some projections rules were applied: whitespace, dash, dots and a couple of commonly confused characters where projected to well-defined codepoints.
The same normalisation was applied to OCR predictions.
At the end of this first stage, an OCR Quality Assessment (Q.A.) between the \emph{normalised} groundtruth text and the
OCR output is performed on the basis of the $8,765$ entries which were manually controlled, totalling $424,764$ characters (including $54,387$ spacing characters). Entries are $49.0$-characters long on average.

>>>>

The directories are available from different libraries in Paris and have been digitised independently in various levels of quality. 
They cover a large period of time and originate from several publishers.
Therefore, their contents, indexes, layouts, methods of printing, etc. may vary a lot from one directory to another (see fig. \ref{fig:directories}).
We want our groundtruth dataset to be representative of the diversity of directories available in the period.

@@

%1. Entrée/Sortie de l'OCR
\textbf{OCR stage.} The first stage of the pipeline aims at extracting the raw text from the images. 
Individual image fragments are created from each segmented entry and fed to an OCR system for text extraction.
An entry might span over multiple text lines but is
always a single block. Thus, the most adapted mode is chosen when the OCR system allows for the detection mode (e.g. the
\emph{block} mode for \emph{Tesseract}). 
Some glyphs used in this dataset might be unknown to the OCR, and some like
\scalerel*{\includegraphics{./images/LH.png}}{H} do not even have a Unicode codepoint, and were annotated using Unicode Private User Area 1.
Furthermore, as some annotations guidelines where unclear to human annotators, some projections rules were applied: whitespace, dash, dots and a couple of commonly confused characters where projected to well-defined codepoints.
The same normalisation was applied to OCR predictions.
At the end of this first stage, an OCR Quality Assessment (Q.A.) between the \emph{normalised} groundtruth text and the
OCR output is performed on the basis of the $8,765$ entries which were manually controlled, totalling $424,764$ characters (including $54,387$ spacing characters). Entries are $49.0$-characters long on average.

### 2022-02-28 src-latex/parts/50-ner-xp1-training-set-size-and-pretraining.tex
Make Language Tools happy

\subsection{Results and discussion}
Figure \ref{fig:f1-vs-trainsize} displays the averaged precision, recall, and F1-score for all models on the 8 subsets created from the groundtruth.
CmBERT, CmBERT+ptrn and SpaCy NER display the same behaviour: the performances increase dramatically with the number of training examples and rapidly reach an area of slower progress around 1000 examples.
The F1 score increases by 4.6 points between 49 and 796 examples for CmBERT (resp. 1.6 for CmBERT+ptrn and 5.1 for SpaCy NER) but only by 1 point between 796 and 6373 examples (resp. 0.6 and 1.4).
The models derived from CamemBERT always outperform the SpaCy model.

It appears that pre-training the CamemBERT model on OCR text seems worth it only when a the training set used to fine-tune the NER layer is small.
This effect might be due to the differences in nature between the training subsets, whose texts are manually corrected, and the noisy OCR texts used to pretrain CamemBERT.
Indeed, the learned embeddings from pre-training are specialised to noisy texts and therefore less adapted to clean text.
The pre-training aims at adapting the model to the vocabulary of the domain and to the errors caused by the OCR, which reveals not helpful and even counterproductive when the texts do not contain these types of errors.

>>>>

\subsection{Results and discussion}
Fig. \ref{fig:f1-vs-trainsize} displays the averaged precision, recall, and F1-score for all models on the 8 subsets created from the groundtruth.
CmBERT, CmBERT+ptrn and SpaCy NER display the same behaviour: the performances increase dramatically with the number of training examples and rapidly reach an area of slower progress around 1000 examples.
The F1 score increases by 4.6 points between 49 and 796 examples for CmBERT (resp. 1.6 for CmBERT+ptrn and 5.1 for SpaCy NER) but only by 1 point between 796 and 6373 examples (resp. 0.6 and 1.4).
The models derived from CamemBERT always outperform the SpaCy model.

It appears that pre-training the CamemBERT model on OCR text seems worth it only when the training set used to fine-tune the NER layer is small.
This effect might be due to the differences in nature between the training subsets, whose texts are manually corrected, and the noisy OCR texts used to pretrain CamemBERT.
Indeed, the learned embeddings from pre-training are specialised to noisy texts and therefore less adapted to clean text.
The pre-training aims at adapting the model to the vocabulary of the domain and to the errors caused by the OCR, which reveals not helpful and even counterproductive when the texts do not contain these types of errors.
